Ice sheet mass flows

### 2024-06-24 sankey.tex
Antarctic frontal retreat from Greene (2022)
Closes #11

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED 
        {vML/Mass loss/
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})-
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})},
        {vMG/Mass gain/
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})-
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})}
      },
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}}
    { % mass gain
      \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0},
        at={[yshift=-15mm]f0.left}, anchor=left,
        forked={\qq{f0}/f0i, \Q{vRFZ}/RFZi}}
    }
    { % mass loss
      \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML},
        at={[yshift=-15mm]f0.left}, anchor=left,
        forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}}
    {
      \sankeyfork{f1}{
        \Q{vMG}/MG,
        \Q{vSU}/SU, \Q{vFRET}/FR, \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }
    {
      \sankeyfork{f1}{
        %% \Q{vMG}/MG,
        \Q{vSU}/SU, \Q{vFRET}/FR, \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }

@@

    \sankeynode{name=FRa, quantity=\qq{FR},
      at={[xshift=\xoff]GZa.left}, anchor=right}
    \sankeyoutin{FR}{FRa}

    \sankeynode{name=SUa, quantity=\qq{SU},
      at={[xshift=\xoff]FRa.left}, anchor=right}
    \sankeyoutin{SU}{SUa}

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=\xoff,yshift=8mm]SUa.left}, anchor=right, angle=0}

      \node[font=\tiny, anchor=north]
      at ([yshift=-5mm,xshift=9mm]MGa.bottom) {\qq{MGa}: Accumulation};

@@

      \sankeyadvance[out-red]{FRa}{10mm}
      \sankeyend[out-red]{FRa}
      \sankeyadvance[ice-to-water,out-red]{GZa}{10mm}
      \sankeyend[water,out-red]{GZa}
      \sankeyadvance{D}{10mm}
      \sankeyend{D}

@@

      \belowlabel{RU}{Runoff}
      \belowlabel{BMa}{Basal melting}
      \belowlabel{SUBa}{Submarine melting}
      \belowlabel{D}{Discharge}
      \belowlabel{GZa}{Grounding line retreat}
      \belowlabel{FRa}{Frontal retreat}

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=3mm]SUaa.bottom) {\qq{SUa}: Sublimation};

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=0mm]EVa.bottom) {\qq{EVa}: Evaporation};

@@

  %%   %% DRIFT
  %%   \sankeynode{name=DRIFTo, quantity=33, at={(3mm, -8mm)}, angle=150}
  %%   \sankeynode{name=DRIFTi, quantity=33, at={(-3mm, -8mm)}, angle=210}
  %%   \sankeydubins[minimum radius=5mm]{DRIFTo}{DRIFTi}
  %%   \sankeystart{DRIFTo}
  %%   \sankeyend{DRIFTI}
  %%   \node[anchor=center, align=center, rotate=0, shift=({0,0})] at (0,-15mm) {Drifting (?)};

>>>>

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED 
        {vML/Mass loss/
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRLOSS}+\Q{vGZRET}+\Q{vEV})-
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}+\Q{vFRGAIN})},
        {vMG/Mass gain/
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP}+\Q{vFRGAIN})-
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRLOSS}+\Q{vGZRET}+\Q{vEV})}
      },
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\Q{vFRGAIN}/FG, \qq{f0}/f0i, \Q{vRFZ}/RFZi}}
      }
    } {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\Q{vFRGAIN}/FG, \qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
      }
    }

    \ifthenelse{\Q{vFRGAIN} > 0}{
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=\xoff]FG.left}, anchor=right}
      \sankeystart{FGi}
      \abovelabel{FGi}{Frontal advance}
      \sankeyoutin{FGi}{FG}
    }{}

@@

    \ifthenelse{\Q{vMG} > \Q{vML}}
    {
      \sankeyfork{f1}{
        \Q{vMG}/MG,
        \Q{vSU}/SU,
        \Q{vFRLOSS}/FL,
        \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }
    {
      \sankeyfork{f1}{
        %% \Q{vMG}/MG,
        \Q{vSU}/SU,
        \Q{vFRLOSS}/FL,
        \Q{vGZRET}/GZ,
        \Q{vDYN}/f6, \Q{vBM}/BM, \Q{vRU}+\Q{vEV}/f8, \Q{vRFZ}/RFZo}
    }

@@

    % FLa must exist for placement, but only draw lines if > 0
    \ifthenelse{\Q{vFRLOSS} > 0} {
        \sankeynode{name=FLa, quantity=\qq{FL},
          at={[xshift=\xoff]GZa.left}, anchor=right}
        \sankeyoutin{FL}{FLa}
      }{
        \sankeynode{name=FLa, quantity=\qq{FL},
          at={[yshift=0mm]GZa.left}, anchor=right}
      }

    \sankeynode{name=SUa, quantity=\qq{SU},
      at={[xshift=\xoff]FLa.left}, anchor=right}
    \sankeyoutin{SU}{SUa}

    \ifthenelse{\Q{vFRLOSS} > 0} {
      \sankeyadvance[out-red]{FLa}{10mm}
      \sankeyend[out-red]{FLa}
      \belowlabel{FLa}{Frontal retreat}
    }{}

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=3mm,yshift=-3mm]MG.left}, anchor=left, angle=0}

      \node[font=\tiny, anchor=north]
      at ([yshift=0mm,xshift=3mm]MGa.south) {\qq{MGa}: Accumulation};

@@

      \sankeyadvance[ice-to-water,out-red]{GZa}{10mm}
      \sankeyend[water,out-red]{GZa}
      \sankeyadvance{D}{10mm}
      \sankeyend{D}

@@

      \belowlabel{RU}{Runoff}
      \belowlabel{BMa}{Basal melting}
      \belowlabel{SUBa}{Submarine melting}
      \belowlabel{D}{Discharge}
      \belowlabel{GZa}{Grounding line retreat}

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=3mm]SUaa.east) {\qq{SUa}: Sublimation};

      \node[font=\tiny, anchor=north]
      at ([yshift=-2mm,xshift=0mm]EVa.west) {\qq{EVa}: Evaporation};

@@
